Kinase similarity assessment pipeline for off-target prediction [Article v\versionnumber]

### 2022-06-06 manuscript/manuscript.tex

\begin{figure*}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{kinmap_n_structures_per_kinase.png}
         \caption{Number of PDB structures per kinase. The figure shows the imbalance between highly explored kinases, e.g. groups: TK, CMGC, and CAMK, and less explored ones, e.g. the CK1 group. CDK2 has the most structures, with $426$. The red circle is proportional to the number of PDB structures for each kinase, such that the greater is the circle, the higher is the number of structures.}
         \label{fig:structure_per_kinase}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{kinmap_erlotinib_karaman.png}
         \caption{Developing selective kinase inhibitors is non-trivial since kinases are highly conserved in the ATP binding site. EGFR inhibitor Erlobinib binds not only to its intended target EGFR, but also to kinases in remote groups, such as SLK/LOK in the STE group and GAK in the CMGC group. The blue circle is proportional to the $K_d$ value in \SI{}{\nano\Molar} taken from the \citet{Karaman_2008_NatBiotechnol} dataset.}
         \label{fig:off_target}
     \end{subfigure}
        \caption{Visual representation using the Manning tree of existing challenges in kinase research: un-/underexplored kinase groups (left) and the promiscuity character of kinases (right). The figure is taken from \href{https://projects.volkamerlab.org/teachopencadd/talktorials/T023\_what\_is\_a\_kinase.html}{https://projects.volkamerlab.org/teachopencadd/talktorials/T023\_what\_is\_a\_kinase.html} and is generated using KinMap~\cite{Eid_2017_BMCBioinformatics}.}
        \label{fig:kinmap}
\end{figure*}

>>>>

\begin{figure*}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{kinmap_n_structures_per_kinase.png}
         \caption{Number of PDB structures per kinase. The figure shows the imbalance between highly explored kinases, e.g. groups: TK, CMGC, and CAMK, and less explored ones, e.g. the CK1 group. CDK2 has the most structures, with $426$. The red circle is proportional to the number of PDB structures for each kinase, such that the greater is the circle, the higher is the number of structures.}
         \label{fig:structure_per_kinase}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{kinmap_erlotinib_karaman.png}
         \caption{Developing selective kinase inhibitors is non-trivial since kinases are highly conserved in the ATP binding site. EGFR inhibitor erlotinib binds not only to its intended target EGFR, but also to kinases in remote groups, such as SLK/LOK in the STE group and GAK in the CMGC group. The blue circle is proportional to the $K_d$ value in \SI{}{\nano\Molar} taken from the \citet{Karaman_2008_NatBiotechnol} dataset.}
         \label{fig:off_target}
     \end{subfigure}
        \caption{Visual representation using the Manning tree of existing challenges in kinase research: un-/underexplored kinase groups (left) and the promiscuity character of kinases (right). The figure is taken from \href{https://projects.volkamerlab.org/teachopencadd/talktorials/T023\_what\_is\_a\_kinase.html}{https://projects.volkamerlab.org/teachopencadd/talktorials/T023\_what\_is\_a\_kinase.html} and is generated using KinMap~\cite{Eid_2017_BMCBioinformatics}.}
        \label{fig:kinmap}
\end{figure*}
